Investigating the applications and limits of single particle light scattering using limited detection schemes

### 2022-11-04 Investigation into low light scattering.tex
Add files via upload

	Where the divergence goes to zero if $p_{ideal}=0$, for a single estimation this gives us an idea of both how confident our model is in it's estimation. We sum the divergence of each measurement across the entire simulation to get an idea of how well the model performs across the entire simulation.

	\begin{align}
		K_{l,total} = \sum\limits_{\# =1}^{no. of steps} K_{l,\#}
	\end{align}

	Since our divergence result is a product of our choice of angles we can see analyse how the choice of angles can be altered to improve our estimate.

@@

	\begin{figure}

	\end{figure}

	We first tested how varying the error value would effect our model's efficacy; as can be seen from \figurename{ 3} our model actually benefits from some degree of signal noise. The introduction of noise allows the prediction to correct itself if it strays to much from the correct result, the trade off comes in a reduction in our model's precision and the occurence of random spikes away from the result. To combat these spikes we time averaged our estimation over $10 \ \mu s$ increments to reduce the effects of noise. This significantly reduced the sharp deviations from the correct result while still allowing the model to correct itself if it ever deviates to far from the correct orientation. Our model is therefore capable of taking a noisy signal and converting it into a close approximation of the

>>>>

	Where the divergence goes to zero if $p_{ideal}=0$, for a single estimation this gives us an idea of both how confident our model is in it's estimation. We sum the divergence of each measurement across the entire simulation to get an idea of how well the model performs across the entire simulation. To measure how much our result had improved we compare it to a worse case scenario, where every $\hat{n}$ is given uniform probability, and evaluate the improvement factor $F(K_l)$

	\begin{align}
		K_{l,total} = \sum\limits_{\# =1}^{no. of steps} K_{l,\#}
		F(K_l) = \frac{K_{l,\ worst}}{K_{l,total}}
	\end{align}

	To measure how much our result had improved we compare it to a worse case scenario, where every $\hat{n}$ is given uniform probability. Since our divergence result is a product of our choice of angles we can see analyse how the choice of angles can be altered to improve our estimate.

@@

	We first tested how varying the error value would effect our model's efficacy; calculating the improvement factor $F(K_l)$ with each test.
	As can be seen from \figurename{ 3} our model actually performs better with noisy signals, to the extent that a signal error of $10\%$ resulted in a worse performance than if we had just guessed each orientation at random. 
	\begin{figure}[b]
		\begin{subfigure}{0.33\textwidth}
			\includegraphics[width=\textwidth]{Error_10_percent.png}
			\subcaption{$F(K_l) = 0.9422$}
		\end{subfigure}
		\begin{subfigure}{0.33\textwidth}
			\includegraphics[width=\textwidth]{Error_20_percent.png}
			\subcaption{$F(K_l) = 1.366$}
		\end{subfigure}
		\begin{subfigure}{0.33\textwidth}
			\includegraphics[width=\textwidth]{Error_30_percent.png}
			\subcaption{$F(K_l)=1.440$}
		\end{subfigure}
		\caption{Model predictions with signal error at a) $10 \%$, b)  $20\%$, and c) $30\%$}
	\end{figure}
